Energy and Momentum of a Density-Driven Overflow in the Samoan Passage

### 2023-02-15 doc/northern_sill_energetics.tex
thank reviewers
retrieve lost changes

\authors{Gunnar Voet,\aff{a}\correspondingauthor{Gunnar Voet, gvoet@ucsd.edu}
Matthew H. Alford,\aff{a}
Jesse M. Cusack,\aff{a,b}
Larry J. Pratt,\aff{c}
James B. Girton,\aff{d}
Glenn S. Carter,\aff{e}
Jody M. Klymak,\aff{f}
Shuwen Tan,\aff{g}
 and Andreas M. Thurnherr\aff{g}
}

\affiliation{\aff{a}{Scripps Institution of Oceanography, University of California San Diego, La Jolla, California}\\
\aff{b}{Rutgers, The State University of New Jersey, New Brunswick, New Jersey}\\
\aff{c}{Woods Hole Oceanographic Institution, Woods Hole, Massachusetts}\\
\aff{d}{Applied Physics Laboratory, University of Washington, Seattle, Washington}\\
\aff{e}{Department of Oceanography, University of Hawaii at M\={a}noa, Honolulu, Hawaii}\\
\aff{f}{University of Victoria, Victoria, British Columbia, Canada}\\
\aff{g}{Lamont-Doherty Earth Observatory, Columbia University, Palisades, New York}\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
We wish to thank John Mickett, Eric Boget, Keith Magness, Trina Litchendorf, Andrew Cookson, Zo\"{e} Parsons, Samuel Fletcher, Andy Pickering, Thomas Decloedt, Kelly Pearson, Janna K\"ohler, Tahmeena Aslam, Deepika Goundar, Tessa Tafua, Alofa Aleta and Vaatele Tauinaola for their assistance in making the measurements; and Captains and crews of R/Vs \emph{Revelle} and \emph{Thompson} for their skill in handling and operating the vessels, without which these measurements would not have been possible.
We are grateful to Zhongxiang Zhao for running an earlier version of the numerical model.
We thank Rob Pinkel and Bill Young for fruitful conversations.
This work was funded by the National Science Foundation under grants OCE-1029268, OCE-1029483, OCE-1657264, OCE-1657795 and OCE-1658027.

>>>>

\authors{Gunnar Voet,\aff{a}\correspondingauthor{Gunnar Voet, gvoet@ucsd.edu}
Matthew H. Alford,\aff{a}
Jesse M. Cusack,\aff{a,b,c}
Larry J. Pratt,\aff{d}
James B. Girton,\aff{e}
Glenn S. Carter,\aff{f}
Jody M. Klymak,\aff{g}
Shuwen Tan,\aff{h,i}
 and Andreas M. Thurnherr\aff{h}
}

\affiliation{\aff{a}{Scripps Institution of Oceanography, University of California San Diego, La Jolla, California}\\
\aff{b}{Rutgers, The State University of New Jersey, New Brunswick, New Jersey}\\
\aff{c}{College of Oceanic and Atmospheric Sciences, Oregon State University, Corvallis, Oregon}
\aff{d}{Woods Hole Oceanographic Institution, Woods Hole, Massachusetts}\\
\aff{e}{Applied Physics Laboratory, University of Washington, Seattle, Washington}\\
\aff{f}{Department of Oceanography, University of Hawaii at M\={a}noa, Honolulu, Hawaii}\\
\aff{g}{University of Victoria, Victoria, British Columbia, Canada}\\
\aff{h}{Lamont-Doherty Earth Observatory, Columbia University, Palisades, New York}\\
\aff{i}{University of California Irvine, Irvine, California}\\
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% ACKNOWLEDGMENTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\acknowledgments
We wish to thank John Mickett, Eric Boget, Keith Magness, Trina Litchendorf, Andrew Cookson, Zo\"{e} Parsons, Samuel Fletcher, Andy Pickering, Thomas Decloedt, Kelly Pearson, Janna K\"ohler, Tahmeena Aslam, Deepika Goundar, Tessa Tafua, Alofa Aleta and Vaatele Tauinaola for their assistance in making the measurements; and Captains and crews of R/Vs \emph{Revelle} and \emph{Thompson} for their skill in handling and operating the vessels, without which these measurements would not have been possible.
We are grateful to Zhongxiang Zhao for running an earlier version of the numerical model.
We thank Rob Pinkel and Bill Young for fruitful conversations.
This work was funded by the National Science Foundation under grants OCE-1029268, OCE-1029483, OCE-1657264, OCE-1657795 and OCE-1658027.
We thank two anonymous reviewers for their comments that helped improve the paper.
